Testing atlantisom: generate survey sampled length comps

### 2019-05-13 StdSurvLengthCompTest.Rmd
correct resnstd name

atf_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
atf_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
atf_resnstd <- resnall[resnstd$species == "Arrowtooth_flounder",]

>>>>

atf_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
atf_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
atf_resnstd <- resnstd[resnstd$species == "Arrowtooth_flounder",]
